---
output: rmarkdown::github_document
editor_options: 
  chunk_output_type: console
---
```{r pkg-knitr-opts, include=FALSE}
hrbrpkghelpr::global_opts()
```

```{r badges, results='asis', echo=FALSE, cache=FALSE}
hrbrpkghelpr::stinking_badges()
```

```{r description, results='asis', echo=FALSE, cache=FALSE}
hrbrpkghelpr::yank_title_and_description()
```

## What's Inside The Tin

The following functions are implemented:

```{r ingredients, results='asis', echo=FALSE, cache=FALSE}
hrbrpkghelpr::describe_ingredients()
```

## Installation

```{r install-ex, results='asis', echo=FALSE, cache=FALSE}
hrbrpkghelpr::install_block()
```

## Usage

```{r lib-ex}
library(lizzard)

# current version
packageVersion("lizzard")

```

- `index.html` is a static copy of a blog main page with a bunch of `<div>`s with article snippets
- `index1.html` is the same file as `index.htmnl` with a changed cache timestamp at the end
- `index2.html` is the same file as `index.html` with one article snippet removed
- `RMacOSX-FAQ.html` is the CRAN 'R for Mac OS X FAQ'

```{r}
(h1 <- min_hash_for_file(system.file("extdat", "index.html", package = "lizzard")))

(h2 <- min_hash_for_file(system.file("extdat", "index1.html", package = "lizzard")))

(h3 <- min_hash_for_file(system.file("extdat", "index2.html", package = "lizzard")))

(h4 <- min_hash_for_file(system.file("extdat", "RMacOSX-FAQ.html", package = "lizzard")))

str(h4, 1)

as.character(h4)

str(as_lzjd_hash(as.character(h4)), 1)

identical(as_lzjd_hash(as.character(h4)), h4)

compute_similarity(h1, h1)
compute_distance(h1, h1)

compute_similarity(h1, h2)
compute_distance(h1, h2)

compute_similarity(h1, h3)
compute_distance(h1, h3)

compute_similarity(h1, h4)
compute_distance(h1, h4)

compute_similarity(h2, h3)
compute_distance(h2, h3)

compute_similarity(h2, h4)
compute_distance(h2, h4)

compute_similarity(h3, h4)
compute_distance(h3, h4)
```

## lizzard Metrics

```{r cloc, echo=FALSE}
cloc::cloc_pkg_md()
```

## Code of Conduct

Please note that this project is released with a Contributor Code of Conduct. 
By participating in this project you agree to abide by its terms.
